Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets

### 2012-12-03 paper/paper.tex
bib for paper and some formatting

This set of keywords clearly allows a large number of false positives:\\
\begin{quote}
nice fish and chip.. good pie apple :-) http://t.co/KVDN5r5l \\
20 chicken nuggets, chips, big mac, and a vanilla milkshake LIFE IS GOOD \\
1 more day whoop plus safari ride yay \\
Ashley staples an apple.  "AHHHH!!!!  Apple juice in my eye!" \\
I ain't seen uncle Mac in a while \\
\end{quote}

We define a tweet to be "about" Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers. We make the assumption that spam will be filtered from the testing set. This could be done via an existing Naive Bayes classifier, but we simply did not include instances of spam in our corpus during the manual labeling process. We collected our tweets over the course of twelve hours. On Twitter, a single message posted is often reposted, or "re-tweeted," many more times in a very short timespan. Because of the small timespan of our data collection, a large number of retweets (effectively duplicates) appeared in the dataset. We filtered these duplicates out of the dataset as well to prevent over-fitting in our model. After filtering, our original set of 115,000 tweets was reduced to 65,000. A representative sample of non-spam, non-duplicate tweets has composition of 60\% topical instances and 40\% false positives [need to analyze this for sure].
\begin{quote}
A computer-posted spam tweet: I've collected 10,650 gold coins! http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
A retweet, signified by "RT": RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
\end{quote}

@@

\subsubsection{Feature-space Enrichment}
~\\
\textit{Stopword removal}: We wrote a Pipe to remove any tokens that appeared in a list of the 50 most common words in the English language.\\
~\\
\textit{N-grams}: Using n-grams is a common method of increasing the number of features present in short text [FIND CITATION]. Often, this is enough to increase accuracy significantly. During our testing, this was not the case. Rather, including bigrams and trigrams actually reduced accuracy slightly.\\
~\\
\textit{HTML corrections}: When accessing tweets through Twitter's public API, the native JSON format includes HTML-encoded entities that can add confusing features to the tweets if not un-escaped. For instance, angle brackets are replaced with \&lt; and \&gt; (less-than and greater-than), causing emoticons, for instance, to no longer be parseable. The emoticon ">.<", for instance, would be "\&gt;.\&lt;". This Pipe un-escapes all such entities, making them easier to parse.\\
~\\
\textit{URL replacement}: 
~\\
\textit{Spell checking}: Twitter's user-generated content contains a large volume of misspelled words. Using a spell-checking library, we wrote a Pipe to replace unrecognized words (misspelled words) with their corrections if the confidence for correction was above a certain threshold. \\
~\\
\subsubsection{Disambiguation}
~\\
\textit{Stemming}: Stemming is the process of reducing words to their "stem." While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem. Therefore the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not the true linguistic stem. We used the standard Porter stemmer to implement this[CITATION].\\

@@

\section{References}
\bibliographystyle{plain}
\bibliography{references}

>>>>

This set of keywords clearly allows a large number of false positives:

\begin{table}[h]
\centering
\begin{tabular}{|l|}
	\hline
	nice fish and chip.. good pie apple :-) \\ http://t.co/KVDN5r5l \\ \hline
	20 chicken nuggets, chips, big mac, and a \\ vanilla milkshake LIFE IS GOOD \\ \hline
	1 more day whoop plus safari ride yay \\ \hline
	Ashley staples an apple.  "AHHHH!!!! \\ Apple juice in my eye!" \\ \hline
	I ain't seen uncle Mac in a while \\
	\hline
\end{tabular}
\caption{Examples of false positive tweets}
\label{tab:myfirsttable}
\end{table}

We define a tweet to be "about" Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers. We make the assumption that spam will be filtered from the testing set. This could be done via an existing Naive Bayes classifier, but we simply did not include instances of spam in our corpus during the manual labeling process. We collected our tweets over the course of twelve hours. On Twitter, a single message posted is often reposted, or "re-tweeted," many more times in a very short timespan. Because of the small timespan of our data collection, a large number of retweets (effectively duplicates) appeared in the dataset. We filtered these duplicates out of the dataset as well to prevent over-fitting in our model. After filtering, our original set of 115,000 tweets was reduced to 65,000. A representative sample of non-spam, non-duplicate tweets has composition of 60\% topical instances and 40\% false positives [need to analyze this for sure].

A computer-posted spam tweet:
\begin{quote}
I've collected 10,650 gold coins! http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
\end{quote}

A retweet, signified by "RT":
\begin{quote}
RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
\end{quote}

@@

\subsubsection{Feature-space Enrichment} ~\\
\textit{Stopword removal}: We wrote a Pipe to remove any tokens that appeared in a list of the 50 most common words in the English language.\\
~\\
\textit{N-grams}: Using n-grams is a common method of increasing the number of features present in short text [FIND CITATION]\cite{article_label,book_label}. Often, this is enough to increase accuracy significantly. During our testing, this was not the case. Rather, including bigrams and trigrams actually reduced accuracy slightly.\\
~\\
\textit{HTML corrections}: When accessing tweets through Twitter's public API, the native JSON format includes HTML-encoded entities that can add confusing features to the tweets if not un-escaped. For instance, angle brackets are replaced with \&lt; and \&gt; (less-than and greater-than), causing emoticons, for instance, to no longer be parseable. The emoticon \">.<", for instance, would be "\&gt;.\&lt;". This Pipe un-escapes all such entities, making them easier to parse.\\
~\\
\textit{URL replacement}: 
~\\
\textit{Spell checking}: Twitter's user-generated content contains a large volume of misspelled words. Using a spell-checking library, we wrote a Pipe to replace unrecognized words (misspelled words) with their corrections if the confidence for correction was above a certain threshold. \\
~\\
\subsubsection{Disambiguation}
~\\
\textit{Stemming}: Stemming is the process of reducing words to their "stem." While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem. Therefore the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not the true linguistic stem. We used the standard Porter stemmer to implement this[CITATION].\\

@@

\bibliographystyle{plain}

\begin{thebibliography}{2}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
\providecommand{\doi}[1]{doi: #1}\else
\providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[{Surname}(2007{\natexlab{a}})]{article_label}
Firstname~I. {Surname}.
\newblock Title of article.
\newblock \emph{Journal of Publication}, 1:\penalty0 1--2, May
2007{\natexlab{a}}.

\bibitem[{Surname2}(2007{\natexlab{b}})]{book_label}
Firstname~I. {Surname}.
\newblock \emph{Title of Book}.
\newblock Publishing House, Address of Publishing House, 1 edition,
2007{\natexlab{b}}.

\end{thebibliography}
